---
output: 
  md_document:
    variant: gfm
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, collapse = TRUE)
```

## Overview

Before installing the RDataXMan package, please make sure the latest version of 
Oracle Java JDK has been installed:

1. Go to https://www.oracle.com/java/technologies/javase-jdk15-downloads.html
2. Go to the download page for the installer of latest Java JDK by following the 
"JDK Download" link.
3. Download the appropriate installer.
    - Windows users should choose "Windows x64 Installer".
    - macOS users should choose "macOS Installer".

After successfully installing Java JDK, macOS users need to open the terminal
and execute the following commands to configure the path to Java:

```{bash eval=FALSE}
sudo R CMD javareconf –n
sudo ln -s $(/usr/libexec/java_home)/jre/lib/server/libjvm.dylib /usr/local/lib
```

After the steps above, both Windows and macOS users can use the following code 
to first install the rJava package from CRAN and then install the RDataXMan 
package from GitHub repository:

```{r eval=FALSE}
install.packages("rJava")
# dev.tools package needed to install from GitHub
# install.packages("devtools")
library(devtools)
install_github("nyilin/RDataXMan")
```
